---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  cache = TRUE,
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(svysim)
library(tidyverse)
library(scales)
library(glue)
```

The goal of `svysim` is to facilitate creating realistic simulations of (biased) survey sampling.



_Abstract_: Surveys are used to teach sampling distributions and selection biases
   all the time, but illustrating a sampling distribution is difficult (because often
   we only have one survey) and most simulations are unrealistic (because they draw from
   a population with uncorrelated random variables, or because they assume a simple
   random sample from that population. This package 
   provides some ready-made datasets from the CCES and Census-related datasets
   along with some customizable sampling schemes, using DeclareDesign. 
   


## Installation

```{r, eval = FALSE}
remotes::install_github("kuriwaki/svysim")
```

## Usage Example

Make a population dataset that expands the common sample via weights. Though the weights are not frequency weights, we treat it as such for simplicity.

```{r}
pop_wtd <- pop_cces %>% 
  mutate(weight_rounded = ceiling(weight_cumulative)) %>% 
  tidyr::uncount(weights = weight_rounded)

pop_wtd
```


Declare it formally as a population using the `DeclareDesign` package.

```{r}
popn <- DeclareDesign::declare_population(pop_cces)
```

Pick a propensity score. For example to oversample highly educated, the true propensity score we chose is:

```{r}
pscore_highed <- p_highed(pop_wtd)
pscore_eddem <- p_eddem(pop_wtd)
```

```{r pscore-histogram, echo = FALSE, out.width = '90%'}
par(mfrow = c(1, 2))
hist(pscore_highed,
     breaks = 50, 
     las = 1,
     main = "High Ed\nOversample", 
     xlab = "Propensity Score",
     ylab = "")
hist(pscore_eddem,
     breaks = 50, 
     las = 1,
     main = "High Ed and Democrat\nOversample", 
     xlab = "Propensity Score",
     ylab = "")

```


Take Samples, e.g. a 0.1 percent sample with no replacement

```{r}
stat_dem(pop_wtd) # true value

samp0  <- samp_with(pop_wtd, sample_srs, n = 600)
stat_dem(samp0)

samp1  <- samp_with(pop_wtd, sample_highed, n = 600)
stat_dem(samp1)

samp2  <- samp_with(pop_wtd, sample_eddem, n = 600)
stat_dem(samp2)
```

Take Multiple Samples. This will take several minutes depending on how many independent samples we draw.

```{r}
pop_mu <- stat_dem(pop_wtd)
n_surveys <- 500
n_samp <- 600
samps0 <- map_dbl(1:n_surveys, ~ stat_dem(samp_with(pop_wtd, sample_srs, n_samp)))
samps1 <- map_dbl(1:n_surveys, ~ stat_dem(samp_with(pop_wtd, sample_highed, n_samp)))
samps2 <- map_dbl(1:n_surveys, ~ stat_dem(samp_with(pop_wtd, sample_eddem, n_samp)))
```


Plot the Sampling Distributions

```{r sampling-dist, out.width = '90%'}
library(scales)
library(glue)

sampling_df <- bind_rows(
  tibble(method = "SRS", muhat = samps0),
  tibble(method = "Education Bias", muhat = samps1),
  tibble(method = "Ed. + PID Bias", muhat = samps2),
) %>% 
  mutate(method = fct_inorder(method))

txt <- glue("Truth: {percent(pop_mu, accuracy = 0.1)}\n",
             "SRS Mean: {percent(mean(samps0), accuracy = 0.1)}\n",
             "Educaton Biased Mean: {percent(mean(samps1), accuracy = 0.1)}\n",
            "Ed. + PID Biased Mean: {percent(mean(samps2), accuracy = 0.1)}")

sampling_df %>%
  ggplot(aes(x = muhat, fill = method)) +
  geom_histogram(alpha = 0.5, 
                 aes(y = stat(width*density)), 
                 position = position_identity(),
                 bins = 25) +
  geom_vline(xintercept = pop_mu, linetype = "dashed") +
  annotate("text", x = pop_mu, y = Inf, label = txt, 
           hjust = 0, vjust = 1.2) +
  theme_minimal() +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = "Estimated Proportion of Democrats in the Population",
       fill = "Sampling Method",
       y = "Proportion",
       caption = glue("{n_surveys} independent polls (each n = {n_samp}) from the same popualation"))
```



# Related Packages

- `kuriwaki/ccesMRPprep`
- `kuriwaki/ddi`
- `kuriwaki/sparseregMRP`
- `kuriwaki/synthArea`
