---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  cache = TRUE,
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(svysim)
library(tidyverse)
library(scales)
library(glue)
```

# svysim


The goal of svysim is to facilitate creating realistic simulations of (biased) survey sampling.

## Installation

```{r, eval = FALSE}
remotes::install_github("kuriwaki/svysim")
```

## Example

Make a population dataset that expands the common sample via weights. Though the weights are not frequency weights, we treat it as such for simplicity.

```{r}
pop_wtd <- pop_cces %>% 
  mutate(weight_rounded = ceiling(weight_cumulative)) %>% 
  tidyr::uncount(weights = weight_rounded)
```
Declare it formally as a population

```{r}
popn <- DeclareDesign::declare_population(pop_cces)
```

Pick a propensity score. For example to oversample highly educated, the true propensity score we chose is:

```{r}
pscore <- p_highed(pop_wtd)
```

```{r pscore-histogram, echo = FALSE}
hist(pscore,
     breaks = 50, 
     las = 1,
     main = "True Propensity Score in the Population", 
     xlab = "Propensity Score",
     ylab = "")
```


Take Samples 

```{r}
popn <- declare_population(pop_wtd)
stat_dem(pop_cces) # true value

samp0  <- draw_data(popn + declare_sampling(handler = sample_srs, n = 1000))
stat_dem(samp0)

samp1  <- draw_data(popn + declare_sampling(handler = sample_highed, n = 1000))
stat_dem(samp1)
```

Take Multiple Samples

```{r}
pop_mu <- stat_dem(pop_wtd)
samps0 <- map_dbl(1:1000, ~ stat_dem(samp_with(popn, sample_srs, 1000)))
samps1 <- map_dbl(1:1000, ~ stat_dem(samp_with(popn, sample_highed, 1000)))
```


Plot the Sampling Distributions

```{r}
library(scales)
library(glue)

sampling_df <- bind_rows(
  tibble(method = "SRS", muhat = samps0),
  tibble(method = "Biased", muhat = samps1),
)

txt <- glue("Truth: {percent(pop_mu, accuracy = 0.1)}\n",
             "SRS Mean: {percent(mean(samps0), accuracy = 0.1)}\n",
             "Biased Mean: {percent(mean(samps1), accuracy = 0.1)}")

sampling_df %>%
  ggplot(aes(x = muhat, fill = method)) +
  geom_histogram(alpha = 0.5, 
                 aes(y = stat(width*density)), 
                 position = position_identity(),
                 bins = 25) +
  geom_vline(xintercept = pop_mu, linetype = "dashed") +
  annotate("text", x = Inf, y = Inf, label = txt, hjust = 1.2, vjust = 1.2) +
  theme_minimal() +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = "Estimated Proportion of Democrats in the Population",
       fill = "Sampling Method",
       y = "Proportion",
       caption = "1000 Independent Polls from the Same Popualation")
```

